\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot, % set margins without considering header and footer
    top=2 cm, % seperation between body and page edge from the top
    bottom=2 cm, % seperation between body and page edge from the bottom
    left=2 cm, % seperation between body and page edge from the left
    right=2 cm, % seperation between body and page edge from the right
    footskip=1.0 cm,
]{geometry} 
\usepackage{titlesec, tabularx, array, xcolor, enumitem, fontawesome5, amsmath, hyperref, eso-pic, calc, bookmark, lastpage, changepage, paracol, ifthen, needspace, iftex}
\definecolor{primaryColor}{RGB}{0, 0, 0} 
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi
\usepackage{charter}

% Formatting
\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0} 
\setlength{\parindent}{0pt} 
\pagenumbering{gobble} 
\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]
\titlespacing{\section}{-1pt}{0.3 cm}{0.2 cm}

\begin{document}

% Header
\begin{center}
    {\fontsize{25 pt}{25 pt}\selectfont Rajath Chandrashekar}\\
    \vspace{5 pt}
    {New York, United States} \quad\textbar\quad
    \href{mailto:rajathch@buffalo.edu}{rajathch@buffalo.edu} \quad\textbar\quad
    +1 (716)-253-5088 \quad\textbar\quad
    \href{https://linkedin.com/in/rajath-chandrashekar-80432915a}{linkedin.com/in/rajath-chandrashekar}\\
\end{center}

% Summary
\section{Summary}
Innovative Mechanical Design Engineer with 3+ years of experience in designing and testing complex mechanical systems, including aircraft and medical components. An expertise in the latest advancements in Robotics and AI with a Masters in Robotics. Seeking a challenging R\&D Mechanical Design Engineer role .

% Experience
\section{Experience}
\textbf{Teaching Assistant, University at Buffalo} \hfill \textbf{Sept 2023 – Present}\\
\begin{itemize}
    \item Teaching Assistant in Computer vision, Digital Controls and Flight Dynamics class
    \item Conducted office hours, setting exam papers and assignments from time to time and Evaluating the students.
    \item As a course instructor, I have an expertise in kinematics and dynamics of robots, Transformations, Linear Algebra, and Control.
\end{itemize}

\textbf{Project Fellow, Mechanical Design Engineer, CMTI} \hfill \textbf{July 2019 - December 2022}\\
\begin{itemize}
    \item Planning, designing, manufacturing, procuring and assembling mechanical systems. 
Design and qualification of test beds used in aircraft parts testing.
\item Worked as an R\&D mechanical engineer in the design of pneumatic proportional valves from prototype to production to achieve linear control characteristics for medical industry applications.
\item We extensively used AS9100 quality standards and other ISO standards for design practices and GD\&T.
Detail-oriented with proper documentation through BOM, ECR, product manuals, user manual preparation, and safety manual preparation according to OSHA standard.
\item Worked on projects that included various combinations in hydraulics, pneumatics, high temperature, and vacuum.  
\item Procurement and vendor relations all the way through purchase ethics and best practices to meet deadlines and quality standards.
\item Experience with Lathe, Mill, Bench drill, CNC machining, Sheet Metal Fabrication, Assembly  and 3D printing. 
\end{itemize}

\textbf{Apprentice Trainee, Mechanical Engineer, BEL} \hfill \textbf{March 2018 – Aug 2018}\\
\begin{itemize}
    \item Trained electrical and mechanical engineers in an interdisciplinary environment and collaborated in the innovative redesign of the structural components of the transformer, improving the durability by 15\% through the integration of advanced materials.
    \item Contributed towards the design of transformer mechanical systems considering all the electrical needs.
\end{itemize}

% Projects (Lab)
\section{Projects (Lab)}
\textbf{Learning-Based Controller Design for Humanoid Walking (UB) } \hfill \textbf{Feb 2023 – Present}\\
\begin{itemize}
    \item As a part of the culminating master’s thesis, I am using Deep Reinforcement Learning to train a control policy to make humanoid robot called BRUCE and Unitree GO2 Dog.
    \item Through this project I have gained deep understanding of complexities of bipedal walking controller, and experience working on a real bipedal robot.
    \item Inverse Kinematics, Forward Kinematics using DH and ET methods, State Estimation using Complimentary and Kalman Filters, Low level motion control joint PID Control tuning. 
\end{itemize}

\textbf{Design of Swung Up controller for an Inverted pendulum (UB)}  \hfill \textbf{March 2023 – April 2023}\\
\begin{itemize}
    \item Swing-up controller was designed using energy methods and tested under simulation in MATLAB and SIMULINK.
    \item A model of the inverted pendulum was created based on Lagrange methods to create a state space representation of the pendulum and further the system was linearized.
    \item Robot Control and Dynamics were practically explored.
\end{itemize}

% Projects (Industry)
\section{Projects (Industry)}

\textbf{Design and Development Hydraulic Second Line Test Rig (CMTI)}  \hfill \textbf{July 2019 – Dec 2022}\\
\begin{itemize}
    \item Involved from end to end: From Part-design, manufacturing and component selection to procurement and assembly of hydraulic and mechanical systems and sensor integration and selection.
    \item Preparing functional test procedures and qualification documents, functional and design verification the rigs.
    \item Used F.E.A methods to analyze structural frames.
    \item Created drawings using GD\&T using ANSI Y-14.5, by keeping into account various manufacturing processes.
    \item Foremost  in vendor development activities for creating a reliable supply chain to meet deadlines and quality needs (AS9100 and ISO9001).
\end{itemize}

\textbf{Design and Development of Pneumatic Proportional Valve for Ventilator (CMTI)}  \hfill \textbf{March 2021 – Sept 2022}\\
\begin{itemize}
    \item Created an R\&D road-map for the project and successfully executed it over the span of the project.
    \item Control system behavior predictive Modeling of mechanical system and solenoid coil from first principal equations.
    \item Directly applying concepts from research papers by implementing a genetic algorithm-based design optimization to optimize the control cone geometry of the valve.
    \item The project was a stage for rewarding interdisciplinary collaboration and product design along with cradle to grave ownership, including Testing of the valve using custom test rig for design verification purpose.
    \item Initial proof-of-concept of the valve using additive manufacturing and final proof-of-concept of the valve using machining process.
\end{itemize}

\textbf{Design of Testing setup for Fuel Actuator (CMTI)}  \hfill \textbf{Nov 2019 – Dec 2021}\\
\begin{itemize}
    \item Complete design of an high temperature fuel system with vacuum chamber and induction coil heater to handle JetA1 fuel. 
    \item Design of hydraulic system circuit to handle Jet A1 fuel both at high (270 °C) and low (-10 °C) temperatures.
    \item Created a P.I.D Controller for accurate temperature profiling of the working fluid required for testing.
    \item Filed a Patent for this process, Patent No. 202141005463.
\end{itemize}

% Education
\section{Education}
\textbf{University at Buffalo, NY} \hfill Master of Science in Robotics, 2025 (GPA: 3.9)\\
\textbf{Visvesvaraya Technological University, INDIA} \hfill Bachelor’s in Mechanical Engineering, 2017 (GPA: 4)

% Skills
\section{Skills}
\textbf{Software:} CATIA, SOLIDWORKS, AUTOCAD, MATLAB/SIMULINK, ANSYS Mechanical, CFD,  ROS-1, ROS-2, MuJoCo, DRAKE\\
\textbf{Expertise:} Control Systems, Python, C++, Analytical Problem Solving, Embedded C, FEA, GD\&T, RL, PPO, Real Robot Experience, Sheet Metal, Machining, 3D Printing and Still counting ....

\end{document}
